\subsection{log (working title)}

When a reader detects a moving object it records a log. 
A reading is of the following format \textless $readerID,objectID,timestamp$ \textgreater.
The \textit{readerID} is the identity of the reader, \textit{objectID} is the identity of the object which is in the range of the reader, and the \textit{timestamp} t is the time where the reader detected the object.
This recording is done at a given sampling rate. 
The same object might be recorded several times by the same reader in a row. 
A reader creates a log for each object that is in the vicinity of the reader thus there can be several logs with the same \textit{timestamp}.

From this log data two different formats of outputs are created.
All data from the readers are continuously streamed to a database that is responsible for maintaining the data.
If a object enters or leave the range of a reader an output is generated, this have the form
\begin{figure}[H]
\[ \textless readerID,objectID,t,flag \textgreater \]
\caption{On-line Output}
\end{figure}

where \textit{flag} is "`START"' or "`END"' respectivly. 
%When the object is no longer detected by the reader an output is generated. 
Note that when a object in no longer detected by the reader  the \textit{flag} is set to "`END"' the timestamp It contains the last \textit{t} where the object was within the vecinity and .
A second output is generated when  based on the first output. 
It have the format 
\begin{align}
%\textbf{Off-line output:}\\
\textless\textit{$readerID,objectID,t_{first},t_{last}$}\textgreater
\end{align}


 
